---
title: "Steps"
author: "Ze Wang"
date: "5/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```


## Use Blogdown, GitHub, and Netlify (Older)

[summer of Blogdown by Alison Hill](https://summer-of-blogdown.netlify.app/)

### Use the [New Project, GitHub First approach](https://happygitwithr.com/new-github-first.html)

1. Create a reposity on GitHub
2. Make a new RStudio project via git clone
3. Make changes locally, save, and commit
4. Push local changes to GitHub (remember to pull changes from GitHub before attempting to push)
5. Deploy on Netlify. Create a new sit from Git on Netlify. *Using GitHub account when signing up for Netlify*.


### After cloning GitHub repository as an RStudio prject

1. Install and load `blogdown` package
2. Create a new site

```{r, eval = FALSE}
library(blogdown)
blogdown::new_site(# theme = "wowchemy/starter-academic",  #<< "theme" is a GitHub repository
	 theme = "gcushen/hugo-academic",
         sample = TRUE, 
         theme_example = TRUE, 
         empty_dirs = TRUE)
       #  to_yaml = TRUE) # Ze commented out this line
blogdown::build_site() # build the website
blogdown::serve_site() # serve the website locally
```
3. Check Hugo version (may need to restart R after updating)
```{r, eval= FALSE}
# is your version less than the minimum version? Version 0.55
hugo_version() 
# if yes, then do this
update_hugo(force = TRUE)
```

4. Add a `netlify.toml` file (*this file is already created with the `new_site` function)
```{r, eval = FALSE}
file.create("netlify.toml")
```

5. Open, and put the following in the `netlify.toml` file (*no need*)

[build]
  publish = "public"
  command = "hugo"
[context.production.environment]
  HUGO_VERSION = "0.83.1"
  HUGO_ENV = "production"
  HUGO_ENABLEGITINFO = "true"
[context.branch-deploy.environment]
  HUGO_VERSION = "0.83.1"
[context.deploy-preview.environment]
  HUGO_VERSION = "0.83.1"


5. Update `.gitignore` file (*NO NEED? DOUBLE CHECK*
add 
"public/
Thumbs.db"
(no quotation marks. DOUBLE CHECK if this is the case as I did not find the ".Thumbs.db" in the "public" folder)

6. Commit and Push to GitHub
Check [here] (https://happygitwithr.com/troubleshooting.html) for troubleshooting regarding connecting RStudio, Git, and GitHub
*Do not have a space in the directory or file name!*
*Do not put the Git repo/RStudio Project inside a folder that is managed by Google Drive, DropBox, Microsoft OneDrive, or a network drive.* This seems to be fine.
*Instead, put the repo/Project into a plain directory on your computer*
(Ze's comment: If no file was created in GitHub repository first, when committing the first time, the branch will be named "master". 
If files such as a README was created in GitHub first, the branch is named "main" because GitHub replaced "master" with "main")

To stage all via RStudio, ctrl-A to select all, then tick one box.

*RStudio can be slow to stage a lot of files. Use the Terminal windown in the lower left pane of RStudio and use `git add -A` to stage all changes*

*Remember to serve site before committing to GitHub* because Hugo does not understand R or R Markdown.

7. Link to GitHub in Netlify
In Netlify, click on "New site from Git" --> Continuous Deployment

### Edit Content
`content` folder
see [an example](https://github.com/apreshill/kellykapowski/tree/master/content)



## Newer (May 2021)
**Check [Alison Hill's post](https://alison.rbind.io/post/new-year-new-blogdown/)**

```{r, eval = FALSE}
# remotes::install_github("rstudio/blogdown")
library(blogdown)
usethis::create_project()
blogdown::new_site(theme = "wowchemy/starter-academic")
blogdown::serve_site()
blogdown::new_post(title = "Hi Hugo", 
                     ext = '.Rmarkdown', 
                     subdir = "post")
usethis::use_git()
usethis::use_github() # requires a GitHub PAT
```

```{r, eval = FALSE}
blogdown::check_gitignore()  # Do Not commit the public directory to GitHub for publishing. add the public folder to .gitignore
blogdown::check_content()
blogdown::check_netlify()
rstudioapi::navigateToFile("config.yaml", line = 3) # then change the baseurl
blogdown::check_hugo()
blogdown::check_config()
rstudioapi::navigateToFile("config/_default/menus.toml")
rstudioapi::navigateToFile("content/authors/admin/_index.md")
blogdown::check_site() # run all check_*() functions
```

#### Find free images/icons
[Unsplash](https://unsplash.com/)
[rawpixel](https://www.rawpixel.com/category/53/public-domain)
[falticon](https://www.flaticon.com/)
[icons in "fab" pack] (https://fontawesome.com/icons?d=gallery&p=2&s=brands)
[icons in "fas" or "far" pack] (https://fontawesome.com/icons?d=gallery&p=2&s=regular,solid)
[icons in "ai" pack] (https://jpswalsh.github.io/academicons/)
[emoji icons "emoji" pack](https://github.com/ikatyang/emoji-cheat-sheet/blob/master/README.md)


[difference between "_index.md" and "index.md"] (https://discourse.gohugo.io/t/what-is-the-difference-between-index-md-and-index-md/10330/11)
**_index.md is for when you have multiple pages under a folder like post or when you want to add metadata to a taxonomy term**.

